Paper Figures and Data

### 2020-09-04 Paper Figures/Paper figures Scipts.Rmd
changed figure 1 and 2 by removing luminescence data panel

    legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, 10)))
    prow <- plot_grid(shakingWtPlot+theme(legend.position="none"),staticWtPlot+theme(legend.position="none"),
                      align='v',labels = c("A", "B"),nrow = 1,label_size= 20, label_x = .02, label_y = 1)
    plot_grid(prow,legend,rel_widths = c(3,.6))
    }

#Graph logs
figure1AB<-GraphGrowthCurveLog1("wt")
figure2AB<-GraphGrowthCurveLog1("mut")

```
```{r Figures 1cd, and 2cd}
#data disk difussion
#####
diskFile<-"~/Documents/Whiteley/PROJECTS/PaSaProject/Staph killing assays/disk difussion assays.csv"
diskData <-read.csv(diskFile)
diskData$strain <- factor(diskData$strain, levels = c("wt", "pqsl"))
diskData <- diskData %>% mutate(val1 = value1-6,val2 = value2-6,average = (val1+val2)/2 )#this removes the diameter of the disks
diskDataStats<-diskData %>% group_by(strain, condition, bio.rep) %>% summarise(meanTech = mean(average)) %>% ungroup() %>%group_by(strain, condition) %>% summarise(meanBio = mean(meanTech), SDBio = std.error(meanTech))
diskDataStats$strain <- factor(diskDataStats$strain, levels = c("wt", "pqsl"))
diskDataStats1<-diskDataStats %>% mutate(
  CondStrain = case_when(
    condition == "shaking" & strain == "pqsl" ~ "pqsLShake",
    condition == "shaking" & strain == "wt"~ "wtShake",
    condition == "static" & strain == "pqsl"~ "pqsLStat",
    condition == "static" & strain == "wt"~ "wtStat"))
#####
#t-tests disk difussion
#####
diskWtShaking<-diskData %>% filter(strain == "wt" & condition == "shaking")
diskMutShaking<-diskData %>% filter(strain == "pqsl" & condition == "shaking")
diskWtStatic<-diskData %>% filter(strain == "wt" & condition == "static")
diskMutStatic<-diskData %>% filter(strain == "pqsl" & condition == "static")

@@

#luminesscence data
#####
luminescenceFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Staph killing assays/summary.csv"
luminescenceData <-read.csv(luminescenceFile)
luminescenceData<-luminescenceData %>% group_by(TimePoint, BioReplicate, Condition, Strain) %>% mutate(techMean = mean(Luminescence)) %>% ungroup() %>% group_by(TimePoint, Condition, Strain) %>% mutate(Mean = mean(techMean), SE =std.error(techMean)) %>% ungroup()
#luminescenceData1<-luminescenceData %>%  
#mutate(LogTotals = ifelse(Totals>0, log10(Totals), 0))#this adds up all the data on each slice and then gets the log of that total

luminescenceData1<-luminescenceData %>% mutate(
  CondStrain = case_when(
    Condition == "shaking" & Strain == "pqsL" ~ "pqsLShake",
    Condition == "shaking" & Strain == "wt"~ "wtShake",
    Condition == "static" & Strain == "pqsL"~ "pqsLStat",
    Condition == "static" & Strain == "wt"~ "wtStat"))
#####

#luminescence t-tests
#####
wtStatLuminescence<-luminescenceData1 %>% filter (CondStrain == "wtStat") %>% filter (TimePoint<7 &TechReplicate == 1)  %>% pull(techMean)
wtMixedLuminescence<-luminescenceData1 %>% filter (CondStrain == "wtShake") %>% filter (TimePoint<7 &TechReplicate == 1) %>% pull(techMean)

mutStatLuminescence<-luminescenceData1 %>% filter (CondStrain == "pqsLStat") %>% filter (TimePoint<7 &TechReplicate == 1)%>% pull(techMean)
mutMixedLuminescence<-luminescenceData1 %>% filter (CondStrain == "pqsLShake") %>% filter (TimePoint<7 &TechReplicate == 1)%>% pull(techMean)

@@

tTestDataLuminescence<-list(tTestWtLuminescence,tTestMutLuminescence,tTestStatLuminescence,tTestMixedLuminescence,
                            tTestWtStatVSMutMixedLuminescence,tTestMutStatVSWtMixedLuminescence)
TtestTable<-name <- function(dataPoint) {
  data <-data.frame(dataPoint$data.name, dataPoint$p.value)
}
tTestLuminescenceTable<-bind_rows(map(tTestDataLuminescence, TtestTable))
#####

#plot disk difussion and luminescence 
#####
GraphStaphKilling<-function(Strain1,Strain2){ 
figure1C<-ggplot()+
      geom_errorbar(data=diskDataStats1 %>% filter (strain == Strain1), aes(x = condition, ymin = meanBio - SDBio, ymax = meanBio + SDBio),width = 0)+
      geom_point(data=diskDataStats1 %>% filter (strain == Strain1), aes(x=condition, y=meanBio, shape =condition), size=3)+
      scale_shape_manual(values = c(1,2),limits=c("shaking","static"), 
                     labels = c(bquote(paste(italic('P. aeruginosa'), " mixed")),
                                bquote(paste(italic('P. aeruginosa'), " static"))))+
  #scale_shape_manual(values = c(16,17),limits=c("static", "shaking"), 
      #               labels = c(bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
      #                          bquote(paste(italic('P. aeruginosa '), Delta*"pqsL mixed"))))+
      scale_x_discrete(name ="", breaks = c("static","shaking"), labels =c("Static","Mixed"))+
    ylim(0,17.5)+
  labs( y = "Zone of inhibition (mm)", shape = "") +
      theme_cowplot(12)+
  theme(plot.margin = unit(c(.5,0,0,.3), "cm"),
        axis.text.x  = element_text(margin = margin(0,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11),
        legend.title = element_text(size=13),legend.text = element_text(size = 11))

figure1D<-ggplot()+
      geom_line(data=luminescenceData1 %>% filter (Strain == Strain2) %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, group = Condition), size=.5, show.legend = FALSE)+
      geom_point(data=luminescenceData1%>% filter (Strain == Strain2) %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, shape = Condition), size=3)+
      geom_errorbar(data=luminescenceData1%>% filter (Strain == Strain2) %>% filter (TimePoint<7), aes(x=TimePoint, ymin=Mean-SE,ymax=Mean+SE), width = 0)+
      scale_y_log10(name=expression(paste(italic('S. aureus'), " luminescence (%)" )), limits = c(1,121),labels = c(1, 10, 100),breaks = c(1, 10, 100))+
      labs( x = "Time (minutes)",shape = "") +
      scale_shape_manual(values = c(1,2),limits=c("shaking","static"))+
      theme_cowplot(12)+
      theme(legend.position="top",plot.margin = unit(c(0,0,0,0), "cm"),
            axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
            axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))

legendFigure1C <- get_legend(figure1C + theme(legend.box.margin = margin(0, 0, 0, 10)))
plotsFigure1cd <- plot_grid(figure1C+theme(legend.position="none"),figure1D+theme(legend.position="none"),
                      align='vh',labels = c("C", "D"),hjust = -1,nrow = 1,label_size= 20)
plot_grid(plotsFigure1cd,legendFigure1C,rel_widths = c(3, .6))
}   
figure1CD<-GraphStaphKilling("wt","wt")
figure2CD<-GraphStaphKilling("pqsl", "pqsL")
#####
```

@@

test1Unique$LogBin <- factor(test1Unique$LogBin, levels = c("(5, 10]","(10, 100]",paste0("(100, ",bquote("\U221E"), ")")))
test1Unique$ConditionNew <- factor(test1Unique$ConditionNew, levels = c("Mono", "Co"))
#####

@@

#plot frequency bins proportion
test1Unique$Species <- factor(test1Unique$Species, levels = c("Pa", "Sa"),
                                         labels = c('P. aeruginosa','S. aureus'))
PlotFreqLogBinProp<-function(strain){
  df <-test1Unique%>% filter(Strain == strain)
  ggplot()+
    geom_col(data = df, aes(x=LogBin,y=MeanDensityLogBin*100,  fill =ConditionNew ),size=4,position = position_dodge( width = .9))+
    geom_errorbar(data = df,aes(x=LogBin,ymin=(MeanDensityLogBin-SEDensityLogBin)*100, ymax = (MeanDensityLogBin+SEDensityLogBin)*100, group = ConditionNew),width = 0, size= .5,position = position_dodge( width = .9))+
    facet_grid(.~Species)+
    labs(fill = "",y = "Aggregates per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    guides(color = FALSE)+
    scale_y_continuous(expand = expand_scale(mult = c(0, 0.2)))+
    scale_fill_grey(labels = c("Mono-culture", "Co-culture"))+
    theme_half_open()+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
          plot.margin = unit(c(0,.5,0,.5), "cm"),
          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,2,2,0),size=11),
          legend.title = element_text(size=13),legend.text = element_text(size = 11),
          legend.position = c(0.79, 0.60))
  }
figure1F<-PlotFreqLogBinProp("PA14wt")
figure2F<-PlotFreqLogBinProp("PA14mut")

figure1EF<-plot_grid(figure1E,figure1F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
figure2EF<-plot_grid(figure2E,figure2F,rel_widths = c(1,1.2),align='vh',labels = c("E", "F"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)

@@

```{Make full figures 1 and 2}
plots <- align_plots(figure1AB, figure1CD,align = 'vh', axis = 'l')
plot_grid(plots[[1]],plots[[2]],figure1EF, align='vh',nrow = 3, rel_heights = c(1,1,1.5))

plots <- align_plots(figure2AB, figure2CD,align = 'vh', axis = 'l')
plot_grid(plots[[1]],plots[[2]],figure2EF, align='vh',nrow = 3, rel_heights = c(1,1,1.5))
```
```{r figure 3}
MixedAggregateBiomassPlot<-ggplot()+
  #geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=PercentTotalBiomass ),size=1)+
  geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=MeanTotalBiomass),shape = 1, size=4)+
  geom_errorbar(data = combinedMixedAggData,aes(x=Strain.x,ymin=MeanTotalBiomass-SETotalBiomass, ymax =MeanTotalBiomass+SETotalBiomass),size=.2, width = 0)+
  scale_shape_manual(values = c(1,2),name = "", limits=c("PA14wt","PA14mut"))+
  scale_x_discrete(breaks=c("PA14wt","PA14mut"), 
                   labels = c(bquote(paste(italic("P. aeruginosa"), " wt")), bquote(paste(italic(Delta*"pqsL")))))+
    labs(y = "Mixed aggregates biomass (%)", x = "")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),legend.position="none")

@@

sa.paPlot<-
  ggplot()+
  geom_point(data = enrichmentDataSpreadsheet %>% filter(Relation == "Sa->Pa"),aes(y=meanEnrichment, x = Strain),size=4, shape = 1)+
  geom_errorbar(data = enrichmentDataSpreadsheet %>% filter(Relation == "Sa->Pa"),
                aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = 0)+
  #labs( y = bquote(paste("Enrichment distance\n", italic("S. aureus") %->% italic("P. aeruginosa "),"("*mu*"m)")), x = "" ) +
  labs(y = expression(atop("Enrichment distance ",paste(italic("S. aureus") %->% italic("P. aeruginosa "),"("*mu*"m)")))) +
  scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),
                     labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type")),
                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL"))))+
  scale_x_discrete(name =expression(italic("P. aeruginosa")), breaks = c("wt","mut"), 
                   labels = c("wt", bquote(paste(italic(Delta*"pqsL")))))+
  ylim(0, 10)+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),legend.position="none")

sa.saPlot<-
  ggplot()+
  geom_point(data = enrichmentDataSpreadsheet %>% filter(Relation == "Sa->Sa"),aes(y=meanEnrichment, x = Strain),size=4, shape = 1)+
  geom_errorbar(data = enrichmentDataSpreadsheet %>% filter(Relation == "Sa->Sa"),
                aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = 0)+
  labs(y = expression(atop("Enrichment distance ",paste(italic("S. aureus") %->% italic("S. aureus "),"("*mu*"m)"))), x = "" ) +
  scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type")),
                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL"))))+
  scale_x_discrete(name =expression(italic("P. aeruginosa")), breaks = c("wt","mut"), 
                   labels = c("wt", bquote(paste(italic(Delta*"pqsL")))))+
  ylim(0, 10)+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),legend.position="none")

>>>>

    legend <- get_legend(shakingWtPlot + theme(legend.box.margin = margin(0, 0, 0, 0)))
    prow <- plot_grid(shakingWtPlot+theme(legend.position="none"),staticWtPlot+theme(legend.position="none"),
                      align='v',labels = c("A", "B"),nrow = 1,label_size= 20, label_x = .02, label_y = 1)
    plot_grid(prow,legend,rel_widths = c(3,.6))
    }

#Graph logs
figure1AB<-GraphGrowthCurveLog1("wt")
figure2AB<-GraphGrowthCurveLog1("mut")
```
```{r Figures 1cd, and 2cd}
#data disk difussion
#####
diskFile<-"~/Documents/Whiteley/PROJECTS/PaSaProject/Staph killing assays/disk difussion assays.csv"
diskData <-read.csv(diskFile)
diskData$strain <- factor(diskData$strain, levels = c("wt", "pqsl"))
diskData <- diskData %>% mutate(val1 = value1-6,val2 = value2-6,average = (val1+val2)/2 )#this removes the diameter of the disks
diskDataStats<-diskData %>% group_by(strain, condition, bio.rep) %>% summarise(meanTech = mean(average)) %>% ungroup() %>%group_by(strain, condition) %>% summarise(meanBio = mean(meanTech), SDBio = std.error(meanTech))
diskDataStats$strain <- factor(diskDataStats$strain, levels = c("wt", "pqsl"))
diskDataStats1<-diskDataStats %>% mutate(
  CondStrain = case_when(
    condition == "shaking" & strain == "pqsl" ~ "pqsLShake",
    condition == "shaking" & strain == "wt"~ "wtShake",
    condition == "static" & strain == "pqsl"~ "pqsLStat",
    condition == "static" & strain == "wt"~ "wtStat"))
#####
#t-tests disk difussion
#####
diskWtShaking<-diskData %>% filter(strain == "wt" & condition == "shaking")
diskMutShaking<-diskData %>% filter(strain == "pqsl" & condition == "shaking")
diskWtStatic<-diskData %>% filter(strain == "wt" & condition == "static")
diskMutStatic<-diskData %>% filter(strain == "pqsl" & condition == "static")

@@

#luminesscence data
#####
luminescenceFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Staph killing assays/summary.csv" 
luminescenceData <-read.csv(luminescenceFile) 
luminescenceData<-luminescenceData %>% group_by(TimePoint, Condition, Strain) %>% mutate(Mean = mean(Luminescence), SE =std.error(Luminescence)) %>% ungroup()
write.csv(luminescenceData1, "/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Staph killing assays/summary2.csv")
luminescenceData1<-luminescenceData %>% mutate(
  CondStrain = case_when(
    Condition == "shaking" & Strain == "pqsL" ~ "pqsLShake",
    Condition == "shaking" & Strain == "wt"~ "wtShake",
    Condition == "static" & Strain == "pqsL"~ "pqsLStat",
    Condition == "static" & Strain == "wt"~ "wtStat"))
luminescenceData1<-luminescenceData1 %>%  mutate(LogTotals = ifelse(Luminescence>0, log10(Luminescence), 0), rep = (4*(TechReplicate-1))+BioReplicate)#this adds up all the data on each slice and then gets the log of that total
#####

#luminescence t-tests
#####
wtStatLuminescence<-luminescenceData1 %>% filter (CondStrain == "wtStat") %>% filter (TimePoint==10 &TechReplicate == 1)  %>% pull(LogTotals) 
wtMixedLuminescence<-luminescenceData1 %>% filter (CondStrain == "wtShake") %>% filter (TimePoint==10 &TechReplicate == 1) %>% pull(LogTotals)

mutStatLuminescence<-luminescenceData1 %>% filter (CondStrain == "pqsLStat") %>% filter (TimePoint==10 &TechReplicate == 1)%>% pull(LogTotals)
mutMixedLuminescence<-luminescenceData1 %>% filter (CondStrain == "pqsLShake") %>% filter (TimePoint==10 &TechReplicate == 1)%>% pull(LogTotals)

@@

tTestDataLuminescence<-list(tTestWtLuminescence,tTestMutLuminescence,tTestStatLuminescence,tTestMixedLuminescence,
                            tTestWtStatVSMutMixedLuminescence,tTestMutStatVSWtMixedLuminescence)
TtestTable<-name <- function(dataPoint) {
  data <-data.frame(dataPoint$data.name, dataPoint$p.value)
}
tTestLuminescenceTable<-bind_rows(map(tTestDataLuminescence, TtestTable))
#this is only comparing the last time point of the log transformed data

timePoints<-seq(1,10)

DoLm<-function(condstrain, bio){
  rep1Data<-luminescenceData1 %>% filter (CondStrain == condstrain, rep == bio) %>% filter(TimePoint > 1) %>% filter(TimePoint<8)
  #rep1Data<-luminescenceData1 %>% filter (CondStrain == condstrain, rep == bio) %>% filter(TimePoint<7) 
  timePoints<-unique(rep1Data$TimePoint)
  rep1lm<- lm(rep1Data$LogTotals ~ timePoints)
  return(as.numeric(rep1lm$coefficients[[2]]))}

wtStatLuminescenceSlope<- unlist(map2("wtStat", seq(1,8), DoLm))
wtMixedLuminescenceSlope<- unlist(map2("wtShake", seq(1,8), DoLm))
mutStatLuminescenceSlope<- unlist(map2("pqsLStat", seq(1,8), DoLm))
mutMixedLuminescenceSlope<- unlist(map2("pqsLShake", seq(1,8), DoLm))
#Anova
blah<-combine(wtStatLuminescenceSlope,wtMixedLuminescenceSlope,mutStatLuminescenceSlope,mutMixedLuminescenceSlope)
res.aov <- aov(data ~ source, data = blah)
# Summary of the analysis
summary(res.aov)
TukeyHSD(res.aov)

#t-tests
tTestWtLuminescenceSlope<-t.test(x = wtStatLuminescenceSlope, y = wtMixedLuminescenceSlope, paired = T)
tTestMutLuminescenceSlope<-t.test(x = mutStatLuminescenceSlope, y = mutMixedLuminescenceSlope, paired = T)

tTestStatLuminescenceSlope<-t.test(x = wtStatLuminescenceSlope, y = mutStatLuminescenceSlope, paired = T)
tTestMixedLuminescenceSlope<-t.test(x = wtMixedLuminescenceSlope, y = mutMixedLuminescenceSlope, paired = T)

tTestWtStatVSMutMixedLuminescenceSlope<-t.test(x = wtStatLuminescenceSlope, y = mutMixedLuminescenceSlope, paired = T)
tTestMutStatVSWtMixedLuminescenceSlope<-t.test(x = wtMixedLuminescenceSlope, y = mutStatLuminescenceSlope, paired = T)

tTestDataLuminescenceSlope<-list(tTestWtLuminescenceSlope,tTestMutLuminescenceSlope,tTestStatLuminescenceSlope,tTestMixedLuminescenceSlope,
                            tTestWtStatVSMutMixedLuminescenceSlope,tTestMutStatVSWtMixedLuminescenceSlope)

tTestLuminescenceTableLast<-bind_rows(map(tTestDataLuminescenceSlope, TtestTable))

tTestLuminescenceTableLast
#####

#plot disk difussion and luminescence 
#####
GraphStaphKilling<-function(Strain1,Strain2){ 
figure1C<-ggplot()+
      geom_errorbar(data=diskDataStats1 %>% filter (strain == Strain1), aes(x = condition, ymin = meanBio - SDBio, ymax = meanBio + SDBio),width = 0)+
      geom_point(data=diskDataStats1 %>% filter (strain == Strain1), aes(x=condition, y=meanBio), size=3)+
      #scale_shape_manual(values = c(1,2),limits=c("shaking","static"), labels = c(bquote(paste(italic('P. aeruginosa'), " mixed")),bquote(paste(italic('P. aeruginosa'), " static"))))+
  #scale_shape_manual(values = c(16,17),limits=c("static", "shaking"), 
      #               labels = c(bquote(paste(italic('P. aeruginosa '), Delta*"pqsL static")),
      #                          bquote(paste(italic('P. aeruginosa '), Delta*"pqsL mixed"))))+
      scale_x_discrete(name =expression(paste(italic('P. aeruginosa'), 'culture')), breaks = c("static","shaking"), labels =c("Static","Mixed"))+
    ylim(0,15.1)+
  labs( y = "Zone of inhibition (mm)", shape = "") +
      theme_cowplot(12)+

  theme(plot.margin = unit(c(.5,.5,0,.5), "cm"),
        axis.text.x  = element_text(margin = margin(0,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,0,0,0),size=13),
        axis.text.y = element_text(margin = margin(0,0,2,0),size=11),
        legend.title = element_text(size=13),legend.text = element_text(size = 11))
        #legend.position = c(0.79, 0.60))

figure1D<-ggplot()+
      geom_line(data=luminescenceData1 %>% filter (Strain == Strain2) %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, group = Condition), size=.5, show.legend = FALSE)+
      geom_point(data=luminescenceData1%>% filter (Strain == Strain2) %>% filter (TimePoint<7), aes(x=TimePoint, y=Mean, shape = Condition), size=3)+
      geom_errorbar(data=luminescenceData1%>% filter (Strain == Strain2) %>% filter (TimePoint<7), aes(x=TimePoint, ymin=Mean-SE,ymax=Mean+SE), width = 0)+
      scale_y_log10(name=expression(paste(italic('S. aureus'), " luminescence (%)" )), limits = c(.1,121),labels = c(0.1,1, 10, 100),breaks = c(0.1,1, 10, 100))+
      labs( x = "Time (minutes)",shape = "") +
      scale_shape_manual(values = c(1,2),limits=c("shaking","static"))+
      theme_cowplot(12)+
      theme(legend.position="top",plot.margin = unit(c(0,0,0,0), "cm"),
            axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
            axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))

legendFigure1C <- get_legend(figure1C + theme(legend.box.margin = margin(0, 0, 0, 0)))
#plotsFigure1cd <- plot_grid(figure1C+theme(legend.position="none"),figure1D+theme(legend.position="none"), align='vh',labels = c("C", "D"),hjust = -1,nrow = 1,label_size= 20)
##plotsFigure1c <- plot_grid(figure1C+theme(legend.position="none"),legendFigure1C, align='vh',labels = c("C"),rel_widths = c(1,.7),hjust = -1,nrow = 1,label_size= 20,label_x = 0, label_y = 1)
plotsFigure1c <- plot_grid(figure1C+theme(legend.position="none"),align='vh',labels = c("C"),hjust = -1,nrow = 1,label_size= 20,
                           label_x = 0, label_y = 1)
#plot_grid(plotsFigure1cd,legendFigure1C,rel_widths = c(1,.1))
}   
figure1CD<-GraphStaphKilling("wt","wt")
figure2CD<-GraphStaphKilling("pqsl", "pqsL")
#####
```

@@

test1Unique$LogBin <- factor(test1Unique$LogBin, levels = c("(5, 10]","(10, 100]",paste0("(100, ",bquote("\U221E"), ")")))

@@

#plot frequency bins proportion
test1Unique$Species <- factor(test1Unique$Species, levels = c("Pa", "Sa"),labels = c('P. aeruginosa','S. aureus'))
test1Unique$ConditionNew <- factor(test1Unique$ConditionNew, levels = c("Mono", "Co"))
PlotFreqLogBinProp<-function(strain){
  df <-test1Unique%>% filter(Strain == strain)
  ggplot()+
    geom_col(data = df, aes(x=LogBin,y=MeanDensityLogBin*100,  fill =ConditionNew ),size=4,position = position_dodge( width = .9))+
    geom_errorbar(data = df,aes(x=LogBin,ymin=(MeanDensityLogBin-SEDensityLogBin)*100, ymax = (MeanDensityLogBin+SEDensityLogBin)*100, group = ConditionNew),width = 0, size= .5,position = position_dodge( width = .9))+
    facet_grid(.~Species)+
    labs(fill = "",y = "Aggregates per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    guides(color = FALSE)+
    scale_y_continuous(expand = expand_scale(mult = c(0, 0.2)))+
    scale_fill_grey(labels = c("Mono-culture", "Co-culture"))+
    theme_half_open()+
    theme(plot.title = element_text(hjust = 0.5),
          strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
          plot.margin = unit(c(0,.5,0,.5), "cm"),
          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,2,2,0),size=11),
          legend.title = element_text(size=13),legend.text = element_text(size = 11),
          legend.position = c(0.79, 0.60))
  }
figure1F<-PlotFreqLogBinProp("PA14wt")
figure2F<-PlotFreqLogBinProp("PA14mut")

figure1EF<-plot_grid(figure1E,figure1F,rel_widths = c(1,1.2),align='vh',labels = c("D", "E"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)
figure2EF<-plot_grid(figure2E,figure2F,rel_widths = c(1,1.2),align='vh',labels = c("D", "E"),hjust = -1,nrow = 1,label_size= 20, label_x = 0, label_y = .95)

@@

```{Make full figures 1 and 2}
top_Row1<-plot_grid(figure1AB,figure1CD,align='vh',nrow = 1, rel_widths = c(2,1))
plot_grid(top_Row1,figure1EF, align='v',nrow = 2, rel_heights = c(1,1.5))

top_Row2<-plot_grid(figure2AB,figure2CD,align='vh',nrow = 1, rel_widths = c(2,1))
plot_grid(top_Row2,figure2EF, align='v',nrow = 2, rel_heights = c(1,1.5))

```
```{r figure 3}
MixedAggregateBiomassPlot<-ggplot()+
  #geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=PercentTotalBiomass ),size=1)+
  geom_point(data = combinedMixedAggData,aes(x=Strain.x,y=MeanTotalBiomass),shape = 1, size=4)+
  geom_errorbar(data = combinedMixedAggData,aes(x=Strain.x,ymin=MeanTotalBiomass-SETotalBiomass, ymax =MeanTotalBiomass+SETotalBiomass),size=.2, width = 0)+
  scale_shape_manual(values = c(1,2),name = "", limits=c("PA14wt","PA14mut"))+
  scale_x_discrete(breaks=c("PA14wt","PA14mut"), 
                   labels = c(bquote(paste(italic("P. aeruginosa"), " wt")), bquote(paste(italic(Delta*"pqsL")))))+
    labs(y = "Mixed aggregates biomass (%)", x = "")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),legend.position="none")

@@

sa.paPlot<-
  ggplot()+
  geom_point(data = enrichmentDataSpreadsheet %>% filter(Relation == "Sa->Pa"),aes(y=meanEnrichment, x = Strain),size=4, shape = 1)+
  geom_errorbar(data = enrichmentDataSpreadsheet %>% filter(Relation == "Sa->Pa"),
                aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = 0)+
  #labs( y = bquote(paste("Enrichment distance\n", italic("S. aureus") %->% italic("P. aeruginosa "),"("*mu*"m)")), x = "" ) +
  labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("S. aureus") %->% italic("P. aeruginosa "))))) +
  scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),
                     labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type")),
                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL"))))+
  scale_x_discrete(name =expression(italic("P. aeruginosa")), breaks = c("wt","mut"), 
                   labels = c("wt", bquote(paste(italic(Delta*"pqsL")))))+
  ylim(0, 10)+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),legend.position="none")

sa.saPlot<-
  ggplot()+
  geom_point(data = enrichmentDataSpreadsheet %>% filter(Relation == "Sa->Sa"),aes(y=meanEnrichment, x = Strain),size=4, shape = 1)+
  geom_errorbar(data = enrichmentDataSpreadsheet %>% filter(Relation == "Sa->Sa"),
                aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = 0)+
  labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("S. aureus") %->% italic("S. aureus ")))), x = "" ) +
  scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type")),
                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL"))))+
  scale_x_discrete(name =expression(italic("P. aeruginosa")), breaks = c("wt","mut"), 
                   labels = c("wt", bquote(paste(italic(Delta*"pqsL")))))+
  ylim(0, 10)+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),legend.position="none")
